An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-06-07 poly-embed-journal/poly-embed-journal.tex
meeting notes

  By Proposition~\ref{prop:SL-minimum}, the level sets $\{\Gamma_{r^*} \mid r^*\in\R^*\}$ are exactly the projections of the facets of $E_L$, and thus exactly the full-dimensional cells of the induced power diagram.
  % , since if it was a lower-dimensional, it would be a subset of some full-dimensional cell, and we would contradict that $\R^*$ is minimum.
  % Moreover, if any $r \in \R \setminus \R^*$ is full-dimensional, $\Gamma_r$ is exactly equal to $\Gamma_{r^*}$ for some $r^* \in \R^*$ since $\R^*$ is representative.
  For any $r\in\R$, the level set $\Gamma_r$ is a cell of the induced power diagram, and thus contained in some full-dimensional cell $\Gamma_{r^*}$.
\end{proof}
\begin{corollary}\label{cor:finite-minrep-trim}
  Let $\Gamma : \simplex \toto \R$ be an elicitable property with a finite minimum representative set $\R^*$.
  Then $\trimnonred(\Gamma) = \{\Gamma_r \mid r\in\R^*\}$.
\end{corollary}
\begin{proof}
  Let $\Theta = \{\Gamma_r \mid r\in\R^*\}$.
  Let $r\in\R$ be arbitrary.
  From Lemma~\ref{lem:finite-minrep-weakly-dominate}, we have some $r^*\in\R^*$ such that either $\Gamma_r = \Gamma_{r^*}$ or $\Gamma_r \subsetneq \Gamma_{r^*}$.
  In the first case, $\Gamma_r$ is an element of both $\trimnonred(\Gamma)$ and $\Theta$, and in the second, $\Gamma_r$ is an element of neither (by definition of $\trimnonred$ and minimum representative).
  Since both $\trimnonred(\Gamma)$ and $\Theta$ are sets of level sets of $\Gamma$, we conclude $\trimnonred(\Gamma) = \Theta$.
\end{proof}

\begin{restatable}{proposition}{embedtrim}\label{prop:embed-trim}
  Let $\Gamma:\simplex\toto\reals^d$ be an elicitable property.
  The following are equivalent:
  \begin{enumerate}\setlength{\itemsep}{0pt}
  \item $\Gamma$ embeds a elicitable finite property $\gamma:\simplex \toto \R$.
  \item $\trimnonred(\Gamma)$ is a finite set, and $\cup\,\trimnonred(\Gamma) = \simplex$.
  % \\ $\hat\Gamma := \trimnonred(\Gamma)$ is a finite property, and $\cup\,\hat\Gamma) = \simplex$.
  \item There is a finite minimum representative set $\U$ for $\Gamma$.
  \item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$, and $\cup\,\Theta = \simplex$.
  \end{enumerate}
  % \raft{I see why you wanted this addition here, but (a) it's clear from the def of embedding, and (b) we don't have varphi defined.  So let's leave it out.}
  Moreover, when any of the above hold, $\trimnonred(\gamma) = \trimnonred(\Gamma) = \{\Gamma_u \mid u\in\U\} = \Theta$.
\end{restatable}
\btw{Deleted old proof (too messy for me to track) 7 June 21 at 8:47 AM}
\begin{proof}
Let $L$ elicit $\Gamma$, and $\ell$ elicit $\gamma$ if given.

$1 \Rightarrow 2$:
Since $\gamma$ is a finite property, it has a finite minimum representative set $\Sc$.
If $\Gamma$ embeds $\gamma$ with map $\varphi$, then $\Gamma$ also has a finite representative set $\U := \varphi(\Sc)$ and $\{\gamma_s \mid s\in\Sc\} = \{\Gamma_u \mid u\in\U\}$.
\raf{Have to argue $\U$ is a minimum representative set for $\Gamma$.}
\jessie{If $\U$ was not minimum, there would be some $u' = \varphi(s')$ such that $\Gamma(p) \cap \U \setminus \{u'\} \neq \emptyset$ for all $p \in \simplex$. This is true iff $\gamma(p) \cap \Sc \setminus \{s'\}$ is non-empty for all $p \in \simplex$, contradicting the assumption that $\Sc$ is minimum. }
From Corollary~\ref{cor:finite-minrep-trim} on both $\gamma$ and $\Gamma$, we have $\trimnonred(\gamma) = \{\gamma_s \mid s\in\Sc\} = \{\Gamma_u \mid u\in\U\} = \trimnonred(\Gamma)$.

$2 \Rightarrow 3$:
Since $\trimnonred(\Gamma) = \{\Gamma_u \mid [u] \in \U_\equiv \}$ is finite and covers the simplex, $\U_\equiv$ is a finite representative set for $L$.
Consider any set $\U = \{u \mid [u] \in \U_\equiv\}$ to be a selection of elements of $\U_\equiv$ from each equivalence class.
We claim $\trimnonred(\Gamma) = \{\Gamma_u \mid u \in \U_\equiv\} = \{\Gamma_u \mid u \in \U\}$, and the result follows immediately.
%Since $\U$ is generated by selecting elements of $\U_\equiv$, we have $\{\Gamma_u \mid u \in \U_\equiv\} \supseteq \{\Gamma_u \mid u \in \U\}$ by construction.
By construction of $\U$, we just need to show $\{\Gamma_u \mid u \in \U_\equiv\} \subseteq \{\Gamma_u \mid u \in \U\}$; consider any $u \in \U_\equiv$.
%If $u \in \U$, the result follows immediately.
If $u \in \U_\equiv \setminus \U$, then we know there is no report in $u' \in \U$ such that $\Gamma_{u} \subsetneq \Gamma_{u'}$, so we must have some $u' \in \U$ such that $u \equiv u'$.
Therefore, $\Gamma_u = \Gamma_{u'} \in \{\Gamma_{u'} \mid u' \in \U\}$, yielding the result.
Thus, there is a finite minimum representative set $\U$ such that $\trimnonred(\Gamma) = \{\Gamma_u \mid u \in \U\}$ covers the simplex.

@@

$3 \Rightarrow 4$:
Since level sets of elicitable properties are closed, the set $\Theta = \{\Gamma_u \mid u \in \U\}$ yields a finite covering of the simplex.
Moreover, by Lemma~\ref{lem:finite-minrep-weakly-dominate}, we have each level set in $\{\Gamma_u \mid u \in \U\}$ full-dimensional.

@@

$4 \Rightarrow 1$: \jessie{Why not use this? Clears up 4 -> 3 and 3 -> 1 and still have all the equalities}
Consider any set of reports $\U = \{u_1, \ldots, u_k\}$ such that $\Theta = \{\Gamma_{u_1}, \ldots, \Gamma_{u_k}\}$.
Since $\cup \Theta = \simplex$, we have $\U$ a finite representative set for $L$, so $L$ elicits $L|_\U$ by Corollary~\ref{cor:representative-embeds-restriction}, and therefore $\Gamma$ embeds $\gamma := \prop{L|_\U}$.

>>>>

  By Proposition~\ref{prop:SL-minimum}, the level sets $\{\Gamma_{r^*} \mid r^*\in\R^*\}$ are exactly the projections of the facets of $E_L$, and thus exactly the full-dimensional cells of the induced power diagram.
  % , since if it was a lower-dimensional, it would be a subset of some full-dimensional cell, and we would contradict that $\R^*$ is minimum.
  % Moreover, if any $r \in \R \setminus \R^*$ is full-dimensional, $\Gamma_r$ is exactly equal to $\Gamma_{r^*}$ for some $r^* \in \R^*$ since $\R^*$ is representative.
  For any $r\in\R$, the level set $\Gamma_r$ is a cell of the induced power diagram, and thus contained in some full-dimensional cell $\Gamma_{r^*}$.
\end{proof}
\begin{corollary}\label{cor:finite-minrep-trim}
  Let $\Gamma : \simplex \toto \R$ be an elicitable property with a finite minimum representative set $\R^*$.
  Then $\trimnonred(\Gamma) = \{\Gamma_r \mid r\in\R^*\}$.
\end{corollary}
\begin{proof}
  Let $\Theta = \{\Gamma_r \mid r\in\R^*\}$.
n  Let $r\in\R$ be arbitrary.
  From Lemma~\ref{lem:finite-minrep-weakly-dominate}, we have some $r^*\in\R^*$ such that either $\Gamma_r = \Gamma_{r^*}$ or $\Gamma_r \subsetneq \Gamma_{r^*}$.
  In the first case, $\Gamma_r$ is an element of both $\trimnonred(\Gamma)$ and $\Theta$, and in the second, $\Gamma_r$ is an element of neither (by definition of $\trimnonred$ and minimum representative).
  Since both $\trimnonred(\Gamma)$ and $\Theta$ are sets of level sets of $\Gamma$, we conclude $\trimnonred(\Gamma) = \Theta$.
\end{proof}
\begin{corollary}\label{cor:finite-rep-contains-min}
  Let $\Gamma : \simplex \toto \R$ be an elicitable property with a finite representative set $\R'$.
  Then $\R'$ contains a minimum representative set.
  \raf{Let's state this in the main part for losses too}
\end{corollary}
\begin{proof}
  TBD
\end{proof}
\begin{corollary}\label{cor:finite-embed-min-rep}
  Let elicitable $\Gamma : \simplex \toto \reals^d$ embed a finite elicitable property $\gamma:\simplex\toto\R$ via embedding $\varphi$.
  Then $\Sc$ is a minimum representative set for $\gamma$ if and only if $\varphi(\Sc)$ is a minimum representative set for $\Gamma$
\end{corollary}
\begin{proof}
  TBD
  \raf{Have to argue $\U$ is a minimum representative set for $\Gamma$.}
  \jessie{If $\U$ was not minimum, there would be some $u' = \varphi(s')$ such that $\Gamma(p) \cap \U \setminus \{u'\} \neq \emptyset$ for all $p \in \simplex$. This is true iff $\gamma(p) \cap \Sc \setminus \{s'\}$ is non-empty for all $p \in \simplex$, contradicting the assumption that $\Sc$ is minimum. }
  \raf{Use Proposition~\ref{prop:SL-minimum}?}
\end{proof}

\begin{restatable}{proposition}{embedtrim}\label{prop:embed-trim}
  Let $\Gamma:\simplex\toto\reals^d$ be an elicitable property.
  The following are equivalent:
  \begin{enumerate}\setlength{\itemsep}{0pt}
  \item $\Gamma$ embeds a elicitable finite property $\gamma:\simplex \toto \R$.
  \item $\trimnonred(\Gamma)$ is a finite set.%, and $\cup\,\trimnonred(\Gamma) = \simplex$.
  % \\ $\hat\Gamma := \trimnonred(\Gamma)$ is a finite property, and $\cup\,\hat\Gamma) = \simplex$.
  \item There is a finite minimum representative set $\U$ for $\Gamma$.
  \item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$, and $\cup\,\Theta = \simplex$.
  \end{enumerate}
  % \raft{I see why you wanted this addition here, but (a) it's clear from the def of embedding, and (b) we don't have varphi defined.  So let's leave it out.}
  Moreover, when any of the above hold, $\trimnonred(\gamma) = \trimnonred(\Gamma) = \{\Gamma_u \mid u\in\U\} = \Theta$.
\end{restatable}
\btw{Deleted old proof (too messy for me to track) 7 June 21 at 8:47 AM}
\begin{proof}
Let $L$ elicit $\Gamma$, and $\ell$ elicit $\gamma$ if given.

$1 \Rightarrow 2$:
Since $\gamma$ is a finite property, it has a finite minimum representative set $\Sc$.
Let $\varphi$ be the embedding between $\gamma$ and $\Gamma$.
From Corollary~\ref{cor:finite-embed-min-rep}, $\U := \varphi(\Sc)$ is a finite minimum representative set for $\Gamma$.
By definition of embedding, $\{\gamma_s \mid s\in\Sc\} = \{\Gamma_u \mid u\in\U\}$.
From Corollary~\ref{cor:finite-minrep-trim} on both $\gamma$ and $\Gamma$, we have $\trimnonred(\gamma) = \{\gamma_s \mid s\in\Sc\} = \{\Gamma_u \mid u\in\U\} = \trimnonred(\Gamma)$.

$2 \Rightarrow 3$:
\begin{itemize}
\item Trim is finite $\implies$ reports giving you trim are rep $\U'$
\item Exists min rep $\U \subseteq \U'$ from Corollary~\ref{cor:finite-rep-contains-min}
\item Equality of set of level sets from Corollary~\ref{cor:finite-minrep-trim}
\end{itemize}
Since $\trimnonred(\Gamma) = \{\Gamma_u \mid [u] \in \U_\equiv \}$ is finite and covers the simplex, $\U_\equiv$ is a finite representative set for $L$.
Consider any set $\U = \{u \mid [u] \in \U_\equiv\}$ to be a selection of elements of $\U_\equiv$ from each equivalence class.
We claim $\trimnonred(\Gamma) = \{\Gamma_u \mid u \in \U_\equiv\} = \{\Gamma_u \mid u \in \U\}$, and the result follows immediately.
%Since $\U$ is generated by selecting elements of $\U_\equiv$, we have $\{\Gamma_u \mid u \in \U_\equiv\} \supseteq \{\Gamma_u \mid u \in \U\}$ by construction.
By construction of $\U$, we just need to show $\{\Gamma_u \mid u \in \U_\equiv\} \subseteq \{\Gamma_u \mid u \in \U\}$; consider any $u \in \U_\equiv$.
%If $u \in \U$, the result follows immediately.
If $u \in \U_\equiv \setminus \U$, then we know there is no report in $u' \in \U$ such that $\Gamma_{u} \subsetneq \Gamma_{u'}$, so we must have some $u' \in \U$ such that $u \equiv u'$.
Therefore, $\Gamma_u = \Gamma_{u'} \in \{\Gamma_{u'} \mid u' \in \U\}$, yielding the result.
Thus, there is a finite minimum representative set $\U$ such that $\trimnonred(\Gamma) = \{\Gamma_u \mid u \in \U\}$ covers the simplex.

@@

$3 \Rightarrow 4$:
By Lemma~\ref{lem:finite-minrep-weakly-dominate}, we have each level set in $\{\Gamma_u \mid u \in \U\}$ full-dimensional, and union to $\simplex$ by definition of representative.

@@

$4 \Rightarrow 1$: \jessie{Why not use this? Clears up 4 -> 3 and 3 -> 1 and still have all the equalities}
Consider any set of reports $\U = \{u_1, \ldots, u_k\}$ such that $\Theta = \{\Gamma_{u_1}, \ldots, \Gamma_{u_k}\}$.
Since $\cup \Theta = \simplex$, we have $\U$ a finite representative set for $L$, so $L$ elicits $L|_\U$ by Corollary~\ref{cor:representative-embeds-restriction}, and therefore $\Gamma$ embeds $\gamma := \prop{L|_\U}$. 
\raf{Use Cor 4 + 6 again, maybe uniqueness of full-dim level sets from Lemma}
